An FMI-Based Initialization Plugin for INTO-CPS Maestro 2

### 2020-07-01 background.tex
Updated the background section. Now I nede to read through the paper and fix the graphs.

The following definitions correspond to the operations that are permitted in the initialization phase of a co-simulation.
\begin{definition}[Output Computation]\label{def:getout}
The $\fget{c}(\dontcare, \outputvar{c})$ represents the calculation of output $\outputvar{c}$ of $c \in \fmus$. Given a co-simulation state, it checks whether all inputs that feed-through to $\outputvar{c}$ are defined.
\end{definition}

@@

\begin{definition}[Initialization]\label{def:initialization}
  Given a scenario $\tuple{\fmus, \coupling}$, we define the initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ as is a finite ordered sequence of FMU function calls that needs to be performed in the initialization of a co-simulation scenario. The ordered sequence is defined as: $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
  $\functioncall_i \in \initcall_{} = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}} \cup (\bigcup_{l \in loops} \fixedpoint{l}),$
  and $i$ denoting the order of the function call.
  Fixed point is defined in \cref{def:fixedpoint} and
  loops in defined as the set of all non trivial SCC see \cref{def:loop}.
\end{definition}

@@

A graph of the dependencies of a co-simulation scenario is established from the interconnected variables by \cref{def:initialization_graph}. The graph is the foundation for the calculation of the initialization procedure and is therefore referred to as the Initialization Graph. The graph construction is similar to the one in \cite{Gomes2019c} except that the later focuses on the co-simulation step, while this work focus on the initialization phase.

@@

The interconnections of FMU variables can lead to circular dependencies between the variables. An example of this behavior is the car suspension system that is presented in \cref{sec:case_study}. \cref{fig:fmu_cycle} shows the co-simulation scenario of the and the Initialization Graph of the system. The Initialization Graph in \cref{fig:fmu_cycle} is annotated with the strongly connected components.

\begin{figure}
    \centering
    \begin{minipage}{0.55\textwidth}
        \centering
    \includegraphics[width=1\textwidth]{images/fmu_cycle.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.35\textwidth}
        \centering
    \includegraphics[width=1\textwidth]{images/SCC.pdf}
    \end{minipage}
    \caption{An FMU co-simulation scenario and its Initialization Graph}
    \label{fig:fmu_cycle}
\end{figure}

The following definitions formalizes the concept of an algebraic loop in a co-simulation scenario, and define the problem these algebraic loops are introducing.
The definition of strongly connected components is adapted from the semantics of Causal Block Diagrams (see \cite{Gomes2020} for an overview).

\begin{definition}[Algebraic loops] \label{def:loop}
An algebraic loop is defined as a non-trivial strongly connected component of the graph in \cref{def:initialization_graph}.
Formally, a strong connected component satisfies $\set{a,b \in SCC: \mathit{Path}(a,b)}$, where $\mathit{Path}(a,b)$ is true when there's a path (including an empty path) between nodes $a$ and $b$ ($\mathit{Path}(a,a)$ is always true).
An $SCC$ is non trivial when it has more than one node.
\end{definition}

Since the edges of the graph represent dependencies between variables, the value of every variable in a non trivial strong component depends on itself.
Let $X$ denote a vector of one or more variables whose value depends on itself. Then the non trivial strong component forms an equation with the form $F(X, U) = X$, where $F$ denotes the relations between the variables in the loop, and $U$ denotes the variables whose values are calculated elsewhere.
This means that algebraic loops need to be handled using fixed point iterations\cite{Gomes2018}.

An example of a co-simulation scenario where fixed point iteration ia needed can be seen in \cref{fig:fmu_cycle} where the Initialization Graph of the quarter car system from \cref{sec:case_study} is shown.

@@

A fixed point iteration technique is not guaranteed to convergence if the system is unstable. This means that an upper bound of the number of repetitions needs to be established to ensure termination. In case of a non-converging algebraic loop the simulation should be stopped since the result of the co-simulation scenario would not be trustworthy. The criteria of a valid co-simulation scenario is specified in \cref{def:convergence}.

>>>>

The following definitions correspond to the operations that are permitted in the initialization phase of a co-simulation.

\begin{definition}[Output Computation]\label{def:getout}
The $\fget{c}(\dontcare, \outputvar{c})$ represents the calculation of output $\outputvar{c}$ of $c \in \fmus$. Given a co-simulation state, it checks whether all inputs that feed-through to $\outputvar{c}$ are defined.
\end{definition}

@@

\begin{definition}[Fixed Point Computation]\label{def:fixedpoint}
The $\fixedpoint{l}$ represents an order sequence of the setting or getting of all input and output variables of a given non-trivial SCC $l$.
\end{definition}

\begin{definition}[Initialization]\label{def:initialization}
  Given a scenario $\tuple{\fmus, \coupling}$, we define the initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ as is a finite ordered sequence of FMU function calls that needs to be performed in the initialization of a co-simulation scenario. The ordered sequence is defined as: $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
  $\functioncall_i \in \initcall_{} = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}} \cup (\bigcup_{l \in loops} \fixedpoint{l}),$
  and $i$ denoting the order of the function call.
  loops in defined as the set of all non trivial SCC see \cref{def:loop}.
\end{definition}

@@

A graph of the dependencies of a co-simulation scenario is established from the interconnected variables by \cref{def:initialization_graph}. The graph is the foundation for the calculation of the initialization procedure and is therefore referred to as the Initialization Graph. The graph construction is similar to the one in \cite{Gomes2019c}, except the later focuses on a general co-simulation step, while this work focus on the initialization phase.

@@

The interconnections of FMU variables can lead to circular dependencies between the variables. An example of this behavior is the car suspension system that is presented in \cref{sec:case_study}. \cref{fig:fmu_cycle} shows the co-simulation scenario of the and the Initialization Graph of the system. The Initialization Graph in \cref{fig:fmu_cycle} is annotated with the strongly connected components of the graph.

\begin{figure}
    \centering
    \includegraphics[width=1\textwidth]{images/quarter_car_SCC.pdf}
    \caption{An FMU co-simulation scenario of the Quarter car and its Initialization Graph denoted with SCCs}
    \label{fig:fmu_cycle}
\end{figure}

The following definitions formalize the concept of an algebraic loop in a co-simulation scenario and define the problem these algebraic loops are introducing.
The definition of strongly connected components is adapted from the semantics of Causal Block Diagrams (see \cite{Gomes2020} for an overview).

\begin{definition}[Algebraic loops] \label{def:loop}
An algebraic loop is defined as a non-trivial, strongly connected component of the graph in \cref{def:initialization_graph}.
Formally, a strong connected component satisfies $\set{a,b \in SCC: \mathit{Path}(a,b)}$, where $\mathit{Path}(a,b)$ is true when there's a path (including an empty path) between nodes $a$ and $b$ ($\mathit{Path}(a,a)$ is always true).
An $SCC$ is non-trivial when it has more than one node.
\end{definition}

Since the edges of the graph represent dependencies between variables, the value of every variable in a non-trivial strong component depends on itself.
Let $X$ denote a vector of one or more variables whose value depends on itself. The non-trivial strong component forms an equation with the form $F(X, U) = X$, where $F$ denotes the relations between the variables in the loop and $U$ denotes the variables whose values are calculated elsewhere.
This means that algebraic loops need to be handled using fixed point iterations\cite{Gomes2018}.

An example of a co-simulation scenario where fixed point iteration is needed can be seen in \cref{fig:fmu_cycle} where the Initialization Graph of the quarter car system from \cref{sec:case_study} is shown.

@@

A fixed point iteration technique is not guaranteed to convergence if the system is unstable. This means that an upper bound of the number of repetitions needs to be established to ensure termination. In the case of a non-converging algebraic loop, the simulation should be stopped since the result of the co-simulation scenario would not be trustworthy. The criteria of a valid co-simulation scenario are specified in \cref{def:convergence}.

### 2020-07-01 initializationorder.tex
Updated the background section. Now I nede to read through the paper and fix the graphs.

\section{Calculation of an Initialization Order}\label{sc:initilization}
The FMI specification defines certain information about the initialization order described through different states of a co-simulation. The initialization phase covers the two states (in chronological order) defined in the specification:
\begin{itemize}
    \item \textit{Instantiated}
    \item \textit{Initialization Mode}
\end{itemize}
In each of the two states, different groups of FMU variables and parameters are potentially assigned a value. The groups are defined by FMI based on rules of the characteristics of the variables. These rules have been extracted as predicates and used in the implementation. 
Some groups consists of variables and parameters whose value does not depend on other variables. These can be set before entering the \textit{Initialization Mode}. Since these variables have no connections to other FMU variables - meaning they are not represented in the graph of \cref{def:initialization_graph}, the order is insignificant. 
The operations are on the variables of each FMU are grouped to perform the fewest possible operations in the initialization.

In the \textit{Initialization Mode} state, all variables of all FMUs should be defined.
The parameters of each FMU are set first, and the order in which they are set is again insignificant as they are independent.
Afterwards the interconnected variables should be defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops place even more requirements on the initialization strategy. Since each non simple strongly connected components need to be isolated from the other parts on the system in able to apply the fixed point iteration technique.

>>>>

\section{Calculation of an Initialization Order}\label{sc:initilization}
The FMI specification defines certain information about the initialization order described through different states of a co-simulation. The initialization phase covers the two states (in chronological order) defined in the specification:
\begin{itemize}
    \item \textit{Instantiated}
    \item \textit{Initialization Mode}
\end{itemize}
In each of the two states, different groups of FMU variables and parameters are potentially assigned a value. The groups are defined by FMI based on rules of the characteristics of the variables. These rules have been extracted as predicates and used in the implementation. 
Some groups consist of variables and parameters whose value does not depend on other variables. These can be set before entering the \textit{Initialization Mode}. Since these variables have no connections to other FMU variables - meaning they are not represented in the graph of \cref{def:initialization_graph}, the order is insignificant. 
The operations are on the variables of each FMU are grouped to perform the fewest possible operations in the initialization.

In the \textit{Initialization Mode} state, all variables of all FMUs should be defined.
The parameters of each FMU are set first, and the order in which they are set is again insignificant as they are independent.
Afterwards the interconnected variables should be defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops place even more requirements on the initialization strategy. Since each non-trivial strongly connected component needs to be isolated from the other variables of the system to obtain their initial values using fixed point iteration.
